---
title: "Clustering for outlier detection"
author: "Míra Radakovic"
date: "2024-12-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Get data

```{r packages}
#install.packages("pacman")
library(pacman)

# misc
#
p_load(here, kableExtra, scales, modelsummary, countrycode, WDI, zoo)

# tidyverse
#
p_load(dplyr, tidyr, stringr, readr, naniar, patchwork, tidylog, ggplot2,
       ggridges, ggrepel)
```

```{r data}
region_data <- readRDS("MICRODATA_ALLYEAR_PROCESSED.RDS") %>% 
  filter(!is.na(exp), !is.na(hhsize), !is.na(exp_cap_group))

get_consexp_cap <- function(countries, years) {
  
  data <- WDI(country = countries, indicator = c("NE.CON.PRVT.PP.KD", "SP.POP.TOTL"), 
              start = min(years), end = max(years)) %>% 
    dplyr::mutate(iso3c = countrycode(iso2c, origin = "iso2c", destination = "iso3c")) %>% 
    dplyr::rename(hhconsexp2017ppp = `NE.CON.PRVT.PP.KD`,
                  pop = `SP.POP.TOTL`) %>% 
    dplyr::mutate(hhconsexp2017ppp = round(hhconsexp2017ppp / pop))
  
  data_filtered <- data %>%
    dplyr::filter(year %in% years) %>%
    arrange(iso3c, year) %>%
    select(country = iso3c, year, hhconsexp2017ppp)
  
  return(data_filtered)
  
}

# Load consumption expenditure data
consexp_capdata <- get_consexp_cap(unique(region_data$country), unique(region_data$year))

```

## Subset data



```{r subset}
first_subset <- region_data[,c("year", "country", "hhid", "hhweight", "urban", "hhsize", "head_age", "head_literate", "nrooms", "tv", "music", "fridge", "exp", "exp_cap_group")]


# Subset the dataframe to unique country-year
# Create a list of dataframes for each unique Country-Year combination

df_list <- split(first_subset, interaction(first_subset$year, first_subset$country))

df_list <- Filter(function(x) nrow(x) > 0, df_list)

```

## A. LOF clustering

This approach does not work for the datasets that are too big and computationally
this become heavy:
- 2. Brazil 2002
- 3. Brazil 2008
- 4. Brazil 2017
- 9. India 2004
- 10. India 2011
- 13. Mexico 2020
- 18. Russia 2020
- 22. South Africa 2014


```{r LOF packages}
library(cluster)  # For Gower's distance
library(factoextra)  # For visualization
library(dbscan)  # For DBSCAN and OPTICS
library(Rtsne)  # For t-SNE visualization
library(ggplot2)
library(cowplot)
```

```{r LOF function , warning=FALSE}

LOF_process <- function(df, df_name, lof_k = 5, outlier_quantile = 0.95) {
  
  vars_to_process <- c("head_age", "nrooms", "hhsize", "exp")
  
  # Separate urban-rural
  ind_urb <- which(df$urban == 1)
  df_urb <- df[df$urban == 1,]
  rownames(df_urb) <- ind_urb
  df_urb <- df_urb[,vars_to_process]
  
  ind_rur <- which(df$urban == 0)
  df_rur <- df[df$urban == 0,]
  rownames(df_rur) <- ind_rur
  df_rur <- df_rur[,vars_to_process]
  
  
  # Compute Gower distance
  gower_dist_u <- daisy(df_urb, metric = "gower")
  gower_dist_r <- daisy(df_rur, metric = "gower")
    
  # Compute LOF
  lof_scores_u <- lof(as.matrix(gower_dist_u), minPts = lof_k)
  lof_scores_r <- lof(as.matrix(gower_dist_r), minPts = lof_k)
    
  # Add LOF scores to the dataframe
  df_urb$LOF <- lof_scores_u
  df_rur$LOF <- lof_scores_r
  
  
  df_urb$index <- rownames(df_urb)
  df_rur$index <- rownames(df_rur)
  
  combined_df <- rbind(df_urb, df_rur)
  combined_df$index <- as.numeric(combined_df$index)

  # Sort by rownames
  sorted_df <- combined_df[order(combined_df$index), ]

  
  # Plot the data highlighting outliers
  plot(sorted_df$LOF, type = "h", main = df_name)
  abline(h = 3, col = "red", lwd = 2)

  # Save outliers
  outliers <- which(sorted_df$LOF > 3)
  
  
  # Return the plot and other results if needed
  return(outliers)
}
```

Now we apply this method to all dataframes (meaning each country year combination).

```{r LOF Armenia 2018, warning=FALSE}

LOF_outliers <- list()


LOF_outliers[[1]] <- LOF_process(df_list[[1]], names(df_list)[1])

```


```{r LOF Ethipia 2018, warning=FALSE}


LOF_outliers[[5]] <- LOF_process(df_list[[5]], names(df_list)[5])

```
```{r LOF Ghana 2005, warning=FALSE}


LOF_outliers[[6]] <- LOF_process(df_list[[6]], names(df_list)[6])

```
```{r LOF Ghana 2017, warning=FALSE}


LOF_outliers[[7]] <- LOF_process(df_list[[7]], names(df_list)[7])

```

```{r LOF Guatemala 2014, warning=FALSE}


LOF_outliers[[8]] <- LOF_process(df_list[[8]], names(df_list)[8])

```









```{r LOF Cambodia 2014, warning=FALSE}


LOF_outliers[[11]] <- LOF_process(df_list[[11]], names(df_list)[11])

```
```{r LOF Cambodia 2019, warning=FALSE}


LOF_outliers[[12]] <- LOF_process(df_list[[12]], names(df_list)[12])

```
```{r LOF Mongolia 2010, warning=FALSE}


LOF_outliers[[14]] <- LOF_process(df_list[[14]], names(df_list)[14])

```
```{r LOF Mongolia 2021, warning=FALSE}


LOF_outliers[[15]] <- LOF_process(df_list[[15]], names(df_list)[15])

```
```{r LOF Nigeria 2018, warning=FALSE}


LOF_outliers[[16]] <- LOF_process(df_list[[16]], names(df_list)[16])

```
```{r LOF Nepal 2019, warning=FALSE}


LOF_outliers[[17]] <- LOF_process(df_list[[17]], names(df_list)[17])

```
```{r LOF Uganda 2019, warning=FALSE}


LOF_outliers[[19]] <- LOF_process(df_list[[19]], names(df_list)[19])

```
```{r LOF Vietnam 2010, warning=FALSE}


LOF_outliers[[20]] <- LOF_process(df_list[[20]], names(df_list)[20])

```
```{r LOF Vietnam 2020, warning=FALSE}


LOF_outliers[[21]] <- LOF_process(df_list[[21]], names(df_list)[21])

```


## B. KAMILA algorithm

```{r KAMILA packages , warning=FALSE}

#install.packages("kamila")
library(kamila)
#install.packages("ape")
library(ape)
library(plotly)
library(cluster)
#install.packages("htmltools", dependencies = TRUE)
library(htmltools)
```

```{r KAMILA function, warning=FALSE}

KAMILA_outliers <- list()

kamila_process <- function(df, df_name){
  
  set.seed(2)
  # Preprocess
  df <- df[,5:ncol(df)]
  
  categorical_columns <- c("urban", "head_literate", "tv", "music", "fridge", "exp_cap_group")
  continuous_columns <- c("hhsize", "head_age", "nrooms", "exp")
  
  df[categorical_columns] <- lapply(df[categorical_columns], as.factor)
  
  # Clustering
  kamila_model <- kamila(
  conVar = df[continuous_columns], 
  catFactor = df[categorical_columns], 
  numClust = 12,        # Number of clusters
  numInit = 10         # Number of initializations for stability
  )
  
  # PCA
  gower_dist <- daisy(df, metric = "gower")
  
  pcoa_result <- pcoa(as.dist(gower_dist))
  
  pcoa_coords <- as.data.frame(pcoa_result$vectors[, 1:3])
  names(pcoa_coords) <- c("PC1", "PC2", "PC3")
  
  pcoa_coords$Cluster <- as.factor(kamila_model$finalMemb)
  
  # Visualize 3D
  
  fig <- plot_ly(
    data = pcoa_coords,
    x = ~PC1,
    y = ~PC2,
    z = ~PC3,
    color = ~Cluster,
    type = "scatter3d",
    mode = "markers",
    marker = list(size = 5)
  ) %>%
    layout(
      title = df_name
      )
  
  fig

  # 2D plot

  #fig_2 <- ggplot(data = pcoa_coords, aes(x = PC1, y = PC2, color = Cluster)) +
  #  geom_point(size = 3, alpha = 0.8) + # Points with transparency
  #  labs(
  #    title = "2D Clustering Visualization",
  #    x = "Principal Coordinate 1 (PC1)",
  #    y = "Principal Coordinate 2 (PC2)"
  #  ) +
  #  theme_minimal()                  # Clean minimal theme
  
    
  # Detect too small clusters (n<5)
  
  cluster_sizes <- table(kamila_model$finalMemb)

  # Flag outliers in small clusters
  outlier_threshold <- 5 # Define minimum cluster size
  outliers <- which(kamila_model$finalMemb %in% names(cluster_sizes[cluster_sizes < outlier_threshold]))
  
  # Print outlier indices
  return(list(outliers, fig))
  
}
```



```{r KAMILA Armenia 2018}
results <- kamila_process(df_list[[1]], names(df_list)[1])
KAMILA_outliers [[1]] <- results[[1]]
results[[2]]
```
```{r}
KAMILA_outliers [[1]]
```

## C. Traditional 3 sd from mean approach

```{r Standard function}
replace_outliers <- function(data, column, group_column) {
  # Create a copy of the data to avoid modifying the original
  modified_data <- data
  
  # Ensure the grouping column exists
  if (!group_column %in% colnames(data)) {
    stop(paste("Column", group_column, "does not exist in the dataframe."))
  }
  
  # Initialize a vector to store outlier indices
  outlier_indices <- c()
  
  # Iterate over the unique values of the group column
  for (group_value in unique(data[[group_column]])) {
    # Subset the data for the current group
    group_data <- data[data[[group_column]] == group_value, ]
    
    # Compute mean and standard deviation for the group
    mean_val <- mean(group_data[[column]], na.rm = TRUE)
    sd_val <- sd(group_data[[column]], na.rm = TRUE)
    
    # Identify outliers within the group
    is_outlier <- abs(group_data[[column]] - mean_val) > (3 * sd_val)
    
    # Find the indices of the outliers in the original data
    group_indices <- which(data[[group_column]] == group_value & is_outlier)
    outlier_indices <- c(outlier_indices, group_indices)
    
    # Replace outliers with NA in the modified data
    modified_data[[column]][data[[group_column]] == group_value & is_outlier] <- NA
  }
  
  # Count total outliers
  total_outliers <- sum(is.na(modified_data[[column]]) & !is.na(data[[column]]))
  
  return(list(data = modified_data, count = total_outliers, outlier_indices = outlier_indices))
}
```


```{r Standard applied, warning=FALSE}
STANDARD_outliers <- list()

vars_to_process <- c("head_age", "nrooms", "hhsize", "exp")
df_list_clean <- df_list
outlier_count <- data.frame(matrix(0, nrow = length(vars_to_process), ncol = length(df_list)))
colnames(outlier_count) <- names(df_list)
rownames(outlier_count) <- vars_to_process

i <- 0

for (df_name in names(df_list)) {
  i <- i + 1
  df <- df_list[[df_name]]
  for (var in vars_to_process) {
    if (var %in% colnames(df)) {
      result <- replace_outliers(df, var, "urban")
      #result <- replace_outliers(df, var)
      df <- result$data
      outlier_count[var, df_name] <- result$count
    }
  }
  df_list_clean[[df_name]] <- df  # Update the cleaned dataframe in the list
  STANDARD_outliers[[i]] <- result$outlier_indices
}
```


```{r compare LOF and STANDARD}

# Initialize a vector to store the count of common numbers
common_counts <- numeric(length(LOF_outliers))

# Loop over each position in the lists
for (i in 1:length(LOF_outliers)) {
  # Get the vectors at the ith position
  vector1 <- LOF_outliers[[i]]
  vector2 <- STANDARD_outliers[[i]]
  
  # Find the intersection of the two vectors and count the common elements
  common_counts[i] <- length(intersect(LOF_outliers, STANDARD_outliers))
}

# Print the result
print(common_counts)
```

Let's investigate the three methods for the first data frame, Armenia 2018.
```{r}
LOF_outliers[[1]]
```
```{r}
KAMILA_outliers[[1]]
```
```{r}
STANDARD_outliers[[1]]
```
While the standard approach seems sound, all it does is cutting the 'edge' values
for each feature, regardless of any connection to other features of the observation.
The LOF approach considers the closest points to the observation, so it considers 
contextual outliers. However, it can only account for numeric variables.
The Kamila algorithm has the capability to consider categorical and numeric 
variables, however the number of clusters need to be predetermined.


## D. Multiple Linear Regression

We fit a multiple linear regression to explain the variable 'exp'. Then we compare
the difference between the prediction and the actual 'exp' value and where the
residual is more then 2 standard deviations away from the prediction, we flag
as outlier.

```{r Regression package}

library(MASS)
library(car)

```


```{r}

REGRESSION_outliers <- list()

regression_process <- function(df, df_name){
  
  data <- df[, colSums(is.na(df)) < nrow(df)]
  data <- data[,6:ncol(data)-1]
  data <- drop_na(data)

  # Fit the multiple linear regression model
  model <- lm(exp ~ ., data = data)

  # Stepwise selection
  stepwise_model <- stepAIC(model, direction = "both")

  # Summary of the optimized model
  #summary(stepwise_model)

  model <- stepwise_model

  # Check for multicollinearity
  vif_values <- vif(model)  # Variance Inflation Factors
  print(vif_values)

  # Residual diagnostics
  data$standardized_residuals <- rstandard(model)  # Standardized residuals
  data$cooks_distance <- cooks.distance(model)    # Cook's distance
  data$leverage <- hatvalues(model)               # Leverage scores

  # Outlier thresholds
  residual_threshold <- 2  # Standardized residuals > 2 are potential outliers
  cook_threshold <- 4 / nrow(data)  # Common heuristic for Cook's distance
  leverage_threshold <- 2 * (ncol(data) / nrow(data))  # Rule of thumb for leverage
  
  # Flag potential outliers
  data$outlier <- with(data, 
      abs(standardized_residuals) > residual_threshold | 
      cooks_distance > cook_threshold | 
      leverage > leverage_threshold
  )

  # View flagged outliers
  # Get row numbers of outliers
  outliers <- which(data$outlier == TRUE)
  
  return(outliers)
}
```

```{r regression calculation, results = 'hide'}

for (i in 1:length(df_list)){
  REGRESSION_outliers[[i]] <- regression_process(df_list[[i]], names(df_list)[i])
}

names(REGRESSION_outliers) <- names(df_list)

```


## E. Random Forest Outlier detection

We then use a random forest model to do the same as with the multiple linear 
regression.
```{r forest package }

library(randomForest)
```


```{r forest function }

FOREST_outliers <- list()

forest_process <- function(df, df_name){
  
  data <- df[, colSums(is.na(df)) < nrow(df)]
  data <- data[,6:ncol(data)-1]
  data <- drop_na(data)

  # Fit random forest model
  set.seed(123)  # For reproducibility
  rf_model <- randomForest(exp ~ ., data = data, importance = TRUE, ntree = 500)

  # Predict values for exp
  data$predicted_exp <- predict(rf_model)

  # Compute residuals
  data$residuals <- data$exp - data$predicted_exp
  
  # Define residual threshold for outliers
  residual_threshold <- 2 * sd(data$residuals)  # 2 standard deviations
  
  # Flag potential outliers
  data$outlier <- abs(data$residuals) > residual_threshold

  # Get row numbers of outliers
  outlier <- which(data$outlier == TRUE)
  return(outlier)
}

```

```{r forest calculation, results = 'hide', warning=FALSE}

for (i in 1:length(df_list)){
  FOREST_outliers[[i]] <- forest_process(df_list[[i]], names(df_list)[i])
}

names(FOREST_outliers) <- names(df_list)

```
## Find commonly detected outliers

Comparing LOF and Regression there are not too many commonalities.
```{r LOF-Reg comparison}
# Find common elements for each pair of vectors
common_list <- mapply(intersect, LOF_outliers, REGRESSION_outliers, SIMPLIFY = FALSE)

# Print the result
common_list
```
Compare LOF and forest, we again do not find many in the intersection.
```{r LOF-forest compare}
# Find common elements for each pair of vectors
common_list <- mapply(intersect, LOF_outliers, FOREST_outliers, SIMPLIFY = FALSE)

# Print the result
common_list
```
Finally we compare forest and regression, and here we find quite a lot in the
intersect.
```{r Reg-forest compare}

# Find common elements for each pair of vectors
common_list <- mapply(intersect, REGRESSION_outliers, FOREST_outliers, SIMPLIFY = FALSE)

# Print the result
common_sum <- lapply(common_list, length)
common_sum

```
```{r}
reg_len <- lapply(REGRESSION_outliers, length)
percent_common <- mapply(`/`, common_sum, reg_len, SIMPLIFY = FALSE)
percent_common
```
```{r}
mean(unlist(percent_common))
```

Approximately 55% of the regression selected outliers are also selected by the
random forest model as well.

## Extended dataset

The new subsets contain more columns then ebfore to allow the models to detect more 
patterns and interdependencies.
```{r large subset}

large_subset <- region_data[,c("year", "country","admin1", "admin2", "hhid", "hhweight", "urban", "hhsize", "head_age","head_male", "head_literate", "nrooms", "tv", "music", "fridge", "exp",
                               "totbiom_cons", "elec_cons", "gas_cons", "frwd_exp", "frwd_cons", "petrol_exp", "scooter", "car", "publictransport_exp", "publictransport", "washmach", "elec_any" )]





# Subset the dataframe to unique country-year
# Create a list of dataframes for each unique Country-Year combination

df_list_large <- split(large_subset, interaction(large_subset$year, large_subset$country))

df_list_large <- Filter(function(x) nrow(x) > 0, df_list_large)

```

Let's see the continuous columns, where we can do outlier detection.

```{r}
summary(df_list_large[[2]])
```

Continuous columns are: hhsize, head_age, nrooms, exp, totbiom_cons, elec_cons,
gas_cons, frwd_exp, frwd_cons, petrol_exp, publictransport_exp.

```{r continuous variables}
cont_var <- c("hhsize", "head_age", "nrooms", "exp", "totbiom_cons", "elec_cons",
"gas_cons", "frwd_exp", "frwd_cons", "petrol_exp", "publictransport_exp")
```

The regression function
```{r}
# Initialize the output list
REGRESSION_outliers_large <- list()

# Define the modified function
regression_process_large <- function(df, df_name, dependent_columns) {
  
  # Retain non metadata columns
  df <- df[, 7:ncol(df)]
  
  # Subset the data to include only complete cases
  data <- df[, colSums(is.na(df)) < nrow(df)]
  
  # Remove column from list
  dependent_columns <- dependent_columns[!sapply(df[dependent_columns], function(col) all(is.na(col)))]

  
  # Loop through each dependent column
  for (col in dependent_columns) {
    
    # Subset the data to include relevant columns
    #data_subset <- data[, c(col, setdiff(names(data), col))]
    data_subset <- data
    
    # Drop rows with NA values
    data_subset <- drop_na(data_subset)
    
    # drop subset for non metadata columns - done already above
    #data_subset <- data_subset[, 7:ncol(data_subset)]
    
    # Fit the multiple linear regression model
    model <- lm(as.formula(paste(col, "~ .")), data = data_subset)
    
    # Stepwise selection
    stepwise_model <- stepAIC(model, direction = "both")
    
    # Update the model with stepwise selection
    model <- stepwise_model
    
    # Check for multicollinearity (optional, if needed)
    # vif_values <- vif(model)
    # print(vif_values)
    
    # Residual diagnostics
    data_subset$standardized_residuals <- rstandard(model)
    data_subset$cooks_distance <- cooks.distance(model)
    data_subset$leverage <- hatvalues(model)
    
    # Outlier thresholds
    residual_threshold <- 2
    cook_threshold <- 4 / nrow(data_subset)
    leverage_threshold <- 2 * (ncol(data_subset) / nrow(data_subset))
    
    # Flag potential outliers
    data_subset$outlier <- with(data_subset,
      abs(standardized_residuals) > residual_threshold |
      cooks_distance > cook_threshold |
      leverage > leverage_threshold
    )
    
    # Get row numbers of outliers
    outliers <- which(data_subset$outlier == TRUE)
    
    # Store the outliers in the output list
    if (!(df_name %in% names(REGRESSION_outliers_large))) {
      REGRESSION_outliers_large[[df_name]] <- list()
    }
    REGRESSION_outliers_large[[df_name]][[col]] <- outliers
  }
  
  # Return the structured list of outliers
  return(REGRESSION_outliers_large)
}

```

```{r, results = 'hide'}
REG_overall <- list()

for (i in 1:length(df_list_large)){
  REG_overall[[i]] <- regression_process_large(df_list_large[[i]], names(df_list_large)[i], cont_var)
}

#names(REG_overall) <- names(df_list_large)

```

```{r}
REG_overall <- lapply(REG_overall, function(x) x[[1]])
names(REG_overall) <- names(df_list_large)

```

Now the same for random forest.

```{r}
FOREST_outliers_large <- list()

forest_process_large <- function(df, df_name, dependent_columns) {
  
  # Retain non metadata columns
  df <- df[, 7:ncol(df)]
  
  # Remove column from list
  dependent_columns <- dependent_columns[!sapply(df[dependent_columns], function(col) all(is.na(col)))]
  
  # Remove columns with all NA values
  df <- df[, colSums(is.na(df)) < nrow(df)]
  
  
  
  # Initialize an empty list for the dataset
  #FOREST_outliers[[df_name]] <- list()
  
  # Loop through each dependent column
  for (col in dependent_columns) {
    
    # Subset the data to include the dependent column and predictors
    data <- df
    data <- drop_na(data)
    
    
    # Fit random forest model
    set.seed(123)  # For reproducibility
    formula <- as.formula(paste(col, "~ ."))
    rf_model <- randomForest(formula, data = data, importance = TRUE, ntree = 50)
    
    # Predict values for the dependent variable
    data$predicted <- predict(rf_model)
    
    # Compute residuals
    data$residuals <- data[[col]] - data$predicted
    
    # Define residual threshold for outliers
    residual_threshold <- 2 * sd(data$residuals, na.rm = TRUE)  # 2 standard deviations
    
    # Flag potential outliers
    data$outlier <- abs(data$residuals) > residual_threshold
    
    # Get row numbers of outliers
    outliers <- which(data$outlier == TRUE)
    
    # Store the outliers in the output list
    FOREST_outliers_large[[df_name]][[col]] <- outliers
  }
  
  # Return the structured list of outliers
  return(FOREST_outliers_large)
}

```

```{r, results = 'hide'}

#FOREST_overall <- list()

#for (i in 1:length(df_list_large)){
#  FOREST_overall[[i]] <- forest_process_large(df_list_large[[i]], names(df_list_large)[i], cont_var)
#  print(i)
#}



```
```{r}

#FOREST_overall <- lapply(FOREST_overall, function(x) x[[1]])
#names(FOREST_overall) <- names(df_list_large)

```


```{r}
#save(FOREST_overall, file = "FOREST_outliers.rda")
```


```{r}
load("FOREST_outliers.rda")
```

Compare and save the commonly flagged observations.

```{r}
compare_nested_lists <- function(list1, list2) {
  # Initialize the result list
  result <- list()
  
  # Get the common top-level names
  top_level_names <- intersect(names(list1), names(list2))
  
  # Loop through each top-level name
  for (name in top_level_names) {
    # If both elements are lists, compare them recursively
    if (is.list(list1[[name]]) && is.list(list2[[name]])) {
      nested_result <- compare_nested_lists(list1[[name]], list2[[name]])
      # Only include non-empty results
      if (length(nested_result) > 0) {
        result[[name]] <- nested_result
      }
    } else {
      # If they are not lists, compare their values
      common_values <- intersect(list1[[name]], list2[[name]])
      if (length(common_values) > 0) {
        result[[name]] <- common_values
      }
    }
  }
  
  return(result)
}

```


```{r}
COMMON_overall <- compare_nested_lists(REG_overall, FOREST_overall)
```

Replace these commonly detected outliers in the data.
```{r}
replace_with_na <- function(dataframes, structured_list) {
  # Ensure both lists have the same length
  if (length(dataframes) != length(structured_list)) {
    stop("The number of dataframes and structured list elements must match.")
  }
  
  # Loop through the dataframes and structured list
  for (i in seq_along(dataframes)) {
    # Current dataframe and structured list element
    df <- dataframes[[i]]
    lists <- structured_list[[i]]
    
    # Check that the structured list has names
    if (is.null(names(lists))) {
      stop("Structured list elements must have names corresponding to column names.")
    }
    
    # Iterate over the names in the structured list element
    for (col_name in names(lists)) {
      # Check if the column exists in the dataframe
      if (col_name %in% names(df)) {
        # Get the row indices to replace with NA
        row_indices <- lists[[col_name]]
        
        # Replace the specified rows in the column with NA
        df[row_indices, col_name] <- NA
      }
    }
    
    # Update the data frame in the list
    dataframes[[i]] <- df
  }
  
  return(dataframes)
}

```

```{r}
df_list_removed <- replace_with_na(df_list_large, COMMON_overall)
```

Export and save.
```{r}
export_and_zip <- function(dataframes, zip_name = "dataframes.zip") {
  # Create a temporary directory to store CSV files
  temp_dir <- tempdir()
  
  # Export each data frame to a CSV file
  csv_files <- c()  # To store paths of created CSV files
  for (name in names(dataframes)) {
    # Define the CSV file name
    csv_file <- file.path(temp_dir, paste0(name, ".csv"))
    
    # Write the data frame to a CSV file
    write.csv(dataframes[[name]], file = csv_file, row.names = FALSE)
    
    # Add the file to the list of CSV files
    csv_files <- c(csv_files, csv_file)
  }
  
  # Create a zip file containing all CSV files
  zip(zipfile = zip_name, files = csv_files)
  
  # Return the path to the zip file
  return(file.path(getwd(), zip_name))
}

```

```{r}

export_and_zip(df_list_removed, "cleaned_df.zip")

```

## Visualize missingness

```{r}
library(ggplot2)

# Function to calculate percentages
calculate_proportions <- function(data_list, outliers_list) {
  results <- data.frame(
    Dataset = character(),
    Category = character(),
    Percentage = numeric(),
    stringsAsFactors = FALSE
  )
  
  for (i in seq_along(data_list)) {
    df <- data_list[[i]]
    outliers <- outliers_list[[i]]
    dataset_name <- names(data_list)[i]
    
    total_values <- prod(dim(df))
    
    # Calculate missing values
    missing_count <- sum(is.na(df))
    missing_percentage <- (missing_count / total_values) * 100
    
    # Calculate outliers
    outlier_count <- sum(is.na(outliers)) - missing_count
    outlier_percentage <- (outlier_count / total_values) * 100
    
    # Calculate remaining values
    remaining_percentage <- 100 - missing_percentage - outlier_percentage
    
    # Append results
    results <- rbind(
      results,
      data.frame(Dataset = dataset_name, Category = "Missing", Percentage = missing_percentage),
      data.frame(Dataset = dataset_name, Category = "Outliers", Percentage = outlier_percentage),
      data.frame(Dataset = dataset_name, Category = "Remaining", Percentage = remaining_percentage)
    )
  }
  
  return(results)
}

# Function to visualize the proportions
visualize_proportions <- function(proportions_df) {
  ggplot(proportions_df, aes(x = Dataset, y = Percentage, fill = Category)) +
    geom_bar(stat = "identity", position = "stack") +
    labs(
      title = "Proportion of Missing, Outliers, and Remaining Data",
      x = "Dataset",
      y = "Percentage"
    ) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    scale_fill_manual(values = c("Missing" = "yellow", "Outliers" = "red", "Remaining" = "orange"))
}
```

```{r}
proportions_df <- calculate_proportions(df_list_large, df_list_removed)
visualize_proportions(proportions_df)
```



